---
title: 'W241: AI Project Pilot'
subtitle: 'Data Cleaning and EDA'
author: "Zhaoning Yu"
date: "3/24/2018"
output: pdf_document
---

```{r setup, include=FALSE, message=FALSE}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
# knitr::opts_chunk$set(echo = TRUE)

# load packages 
library(Hmisc)              # describe()
library(data.table)
library(foreign)            # ??? what does this package do ????????
library(sandwich)           # vcovHC for robust SE calculation
library(lmtest)             # coeftest 
library(AER)                # ivreg
library(multiwayvcov)       # cluster.vcov()
```

# 1. Read Data

## 1.1 Read Data

```{r}
d1 <- fread('./pilot_results/w241_ai_pilot.csv')
head(d1)
```

## 1.2 Remove useless rows and columns

```{r}
# Save the column names
header <- d1[1,]                             # save the header information

# Remove useless rows
d1 <- d1[-c(1,2)]                           # remove rows 1, 2 (redundent headers)

# Remove useless columns
d2 <- d1[d1$Status != 'Survey Preview']     # remove previews (the ones we used for testing survey)
d2 <- subset(d2, select = -c(RecipientLastName, RecipientFirstName, RecipientEmail, ExternalReference))  # empty columns
d2 <- subset(d2, select = -c(Status, DistributionChannel, UserLanguage))        # columns with the same value for all
head(d2)
```
## 1.3 Ensure correct data types

Note everything is a string in this data frame:

```{r, message=FALSE}
str(d2)
```

Change strings into numeric values:

```{r}
# Turn following columns from string to numeric
d2[, 'Progress'] <- sapply(d2[, 'Progress'], as.numeric)
d2[, 'Duration (in seconds)'] <- sapply(d2[, 'Duration (in seconds)'], as.numeric)
d2[, 'LocationLatitude'] <- sapply(d2[, 'LocationLatitude'], as.numeric)
d2[, 'LocationLongitude'] <- sapply(d2[, 'LocationLongitude'], as.numeric)
d2[, 'mTurkCode'] <- sapply(d2[, 'mTurkCode'], as.numeric)

d2[, 'Q1_1'] <- sapply(d2[, 'Q1_1'], as.numeric)
d2[, 'Q3_1'] <- sapply(d2[, 'Q3_1'], as.numeric)
d2[, 'Q6_1'] <- sapply(d2[, 'Q6_1'], as.numeric)
d2[, 'Q8_1'] <- sapply(d2[, 'Q8_1'], as.numeric)
d2[, 'Q10_1'] <- sapply(d2[, 'Q10_1'], as.numeric)
d2[, 'Q12_1'] <- sapply(d2[, 'Q12_1'], as.numeric)
d2[, 'Q20_1'] <- sapply(d2[, 'Q20_1'], as.numeric)
d2[, 'Q5_1'] <- sapply(d2[, 'Q5_1'], as.numeric)
d2[, 'Q7_1'] <- sapply(d2[, 'Q7_1'], as.numeric)
d2[, 'Q9_1'] <- sapply(d2[, 'Q9_1'], as.numeric)
d2[, 'Q11_1'] <- sapply(d2[, 'Q11_1'], as.numeric)
d2[, 'Q13_1'] <- sapply(d2[, 'Q13_1'], as.numeric)
d2[, 'Q33_1'] <- sapply(d2[, 'Q33_1'], as.numeric)
d2[, 'Q34_1'] <- sapply(d2[, 'Q34_1'], as.numeric)
d2[, 'Q35_1'] <- sapply(d2[, 'Q35_1'], as.numeric)
d2[, 'Q36_1'] <- sapply(d2[, 'Q36_1'], as.numeric)
d2[, 'Q37_1'] <- sapply(d2[, 'Q37_1'], as.numeric)

# Turn 'TRUE' 'FALSE' to 1 and 0
f1 <- function(x) {
  if (x=='True') {
    return(1)
  } else if (x=='False') {
    return(0)
  } else {
    return(NA)
  }
}

d2$Q18 <- sapply(d2$Q18, f1)
d2$Q19 <- sapply(d2$Q19, f1)
d2$Q23 <- sapply(d2$Q23, f1)
d2$Q17 <- sapply(d2$Q17, f1)
d2$Q24 <- sapply(d2$Q24, f1)
d2$Finished <- sapply(d2$Finished, f1)

# Turn 'Yes' 'No' to 1 and 0
f2 <- function(x) {
  if (x=='Yes') {
    return(1)
  } else if (x=='No') {
    return(0)
  } else {
    return(NA)
  }
}

d2$Q31 <- sapply(d2$Q31, f2)

# Turn 'Male' 'Female' to 1 and 0
f3 <- function(x) {
  if (x=='Male') {
    return(1)
  } else if (x=='Female') {
    return(0)
  } else {
    return(NA)
  }
}

d2$Q16 <- sapply(d2$Q16, f3)

# Education into 0, 1, 2, 3, 4
f4 <- function(x) {
  if (x=='Other') {
    return(0)
  } else if (x=='High School') {
    return(1)
  } else if (x=='Bachelors Degree') {
    return(2)
  } else if (x=='0 - 2 years of graduate school') {
    return(3)
  } else if (x=='> 2 years of graduate school'){
    return(4)
  } else {
    return(NA)
  }
}

d2$Q14 <- sapply(d2$Q14, f4)

# Turn income into 1, 2, 3, 4
f5 <- function(x) {
  if (x=='0 - $50,000') {
    return(1)
  } else if (x=='$50,000 - $100,000') {
    return(2)
  } else if (x=='$100,000 - $150,000') {
    return(3)
  } else if (x=='$150,000 or greater') {
    return(4)
  } else {
    return(NA)
  }
}

d2$Q15 <- sapply(d2$Q15, f5)
```

```{r}
f1 <- function(x) {
  if (x=='True') {
    return(1)
  } else if (x=='False') {
    return(0)
  } else {
    return(NA)
  }
}
```



Check dataframe: 

```{r}
str(d2)
```


## 1.4 Rename columns for clarity

```{r}
names(d2)
```


```{r}
setnames(d2, old = c("Duration (in seconds)", "Q1_1","Q3_1", "Q6_1", "Q8_1", "Q10_1","Q12_1", "Q20_1" , "Q5_1" , "Q7_1", "Q9_1" , "Q11_1" , "Q13_1" , "Q18" , "Q19","Q23", "Q17"         , "Q24", "Q33_1" , "Q34_1" , "Q35_1" , "Q36_1" , "Q37_1" , "Q31" ,"Q14",  "Q15", "Q16"), new = c('duration_seconds','AI_educated','AI_attitude', 'control_undesirable', "control_jobs", "control_oversight", "control_recommender", "control_beneficial", "treat_beneficial_1", "treat_undesirable_1", "treat_jobs_1","treat_oversight_1", "treat_recommender_1", "attention_undesirable", "attention_jobs", "attention_oversight", "attention_beneficial", "attention_recommender", "treat_beneficial_2", "treat_undesirable_2", "treat_jobs_2", "treat_oversight_2", "treat_recommender_2", "learn_anything", "education_level", "house_income", "gender" ))
names(d2)
```
## 1.5 Combine 2 treatment columns for each treatment question

```{r}
na.zero <- function (x) {
    x[is.na(x)] <- 0
    return(x)
}
```

```{r}
d2$treat_beneficial_1 <- na.zero(d2$treat_beneficial_1)
d2$treat_beneficial_2 <- na.zero(d2$treat_beneficial_2)
d2$treat_beneficial = d2$treat_beneficial_1 + d2$treat_beneficial_2
d2$treat_beneficial
d2$treat_beneficial[d2$treat_beneficial == 0] <- NA
d2$treat_beneficial
```

```{r}
d2$treat_undesirable_1 <- na.zero(d2$treat_undesirable_1)
d2$treat_undesirable_2 <- na.zero(d2$treat_undesirable_2)
d2$treat_undesirable = d2$treat_undesirable_1 + d2$treat_undesirable_2
d2$treat_undesirable
d2$treat_undesirable[d2$treat_undesirable == 0] <- NA
d2$treat_undesirable
```

```{r}
d2$treat_jobs_1 <- na.zero(d2$treat_jobs_1)
d2$treat_jobs_2 <- na.zero(d2$treat_jobs_2)
d2$treat_jobs = d2$treat_jobs_1 + d2$treat_jobs_2
d2$treat_jobs
d2$treat_jobs[d2$treat_jobs == 0] <- NA
d2$treat_jobs
```

```{r}
d2$treat_oversight_1 <- na.zero(d2$treat_oversight_1)
d2$treat_oversight_2 <- na.zero(d2$treat_oversight_2)
d2$treat_oversight = d2$treat_oversight_1 + d2$treat_oversight_2
d2$treat_oversight
d2$treat_oversight[d2$treat_oversight == 0] <- NA
d2$treat_oversight
```

```{r}
d2$treat_recommender_1 <- na.zero(d2$treat_recommender_1)
d2$treat_recommender_2 <- na.zero(d2$treat_recommender_2)
d2$treat_recommender = d2$treat_recommender_1 + d2$treat_recommender_2
d2$treat_recommender
d2$treat_recommender[d2$treat_recommender == 0] <- NA
d2$treat_recommender
```




# 2. EDA

## 2.1 Duration 

Median for finishing the survey is 153 sec (~ 2.5 mins), minimum is 27 secs, maximum 1491 sec (~25 mins). Most people finish the survey 2-3 mins, most finish within 5 mins.

```{r fig.height=3.5, fig.width=8, echo=FALSE}
par(mfrow=c(1,2))
summary(d2$duration_seconds)
hist(d2$duration_seconds, breaks = 25)
boxplot(d2$duration_seconds)
```

## 2.2 Location (Longitude, Latitude)

Most of the survey takers seem to locate on the west-coast (we can add a US map later to make it clear).
```{r}
plot(d2$LocationLongitude, d2$LocationLatitude)
```


##Too Many samples collected (60 instead of 50)

All codes for mTurk given by Qualtrics are unique.
```{r}
length(unique(d2$mTurkCode)) == nrow(d2)
```

Six of our responses are the same IP address answering twice. Could be two people at same IP address - yes, if you look, often they start the task a few seconds apart and have different answers to baseline questions. May be groups of people working together in person (to help eachother find good hits).
```{r}
second_response <- length(d2$IPAddress) - length(unique(d2$IPAddress))
second_response
```




## 2.3 Baseline Questions

### Q.1: How well educated are you about the current state of artificial intelligence technology?

Median is 3, mean is 3.083.

```{r fig.height=3.5, fig.width=8, echo=FALSE}
par(mfrow=c(1,2))
#ggplot(d2, aes(x=AI_educated)) + geom_histogram(binwidth=1, color="black", fill="white")
hist(d2$AI_educated, breaks = 10)
boxplot(d2$AI_educated)
summary(d2$AI_educated)

```

### Q.3: How do you feel in general about the adoption of artificial intelligence technology?

Median is 4, mean is 3.559, most people feel generally positive towards AI.

```{r fig.height=3.5, fig.width=8, echo=FALSE}
par(mfrow=c(1,2))
summary(d2$AI_attitude)
hist(d2$AI_attitude, breaks = 10)
boxplot(d2$AI_attitude)
```

### Q.31: Did you learn anything new about AI while taking this survey?

The mean is 0.6364, people learned something from the survey.

```{r fig.height=3.5, fig.width=8, echo=FALSE}
par(mfrow=c(1,2))
summary(d2$learn_anything)
hist(d2$learn_anything, breaks = 10)
boxplot(d2$learn_anything)
```

## 2.4 Attention Questions

Q18: T/F AI undesirable effects (AI gains consciousness)

-only 64% of people answered correctly

```{r}
correct_answer = 1 - mean(d2$attention_undesirable, na.rm = TRUE)
correct_answer
```

Q19: T/F Jobs (Paralegal)

-60% of people answered correctly

```{r}
correct_answer = mean(d2$attention_jobs, na.rm = TRUE)
correct_answer
```

Q23: T/F Oversight (Guidelines AI oversight in place already)

-everyone answered correctly

```{r}
correct_answer = 1 - mean(d2$attention_oversight, na.rm = TRUE)
correct_answer
```

Q17: T/F  beneficial (AI used in spam block)

- 85% answered correctly

```{r}
correct_answer = mean(d2$attention_beneficial, na.rm = TRUE)
correct_answer
```

Q24: T/F  Recommender (do not use your personal data)

- 55% answered correctly

```{r}
correct_answer = 1 - mean(d2$attention_recommender, na.rm = TRUE)
correct_answer
```


## 2.5 Covariate Questions

### Q.14: What is the highest level of education that you have completed?

Most went to college, about 1/3 high-school, not many 'other'.

```{r fig.height=3.5, fig.width=8, echo=FALSE}
par(mfrow=c(1,2))
describe(d2$education_level)
hist(d2$education_level, breaks = 10)
boxplot(d2$education_level)
```

### Q.15: Which of the following best describes your annual household income?

Most people in 0-50000 and 50000-100000 brackets.
```{r fig.height=3.5, fig.width=8, echo=FALSE}
par(mfrow=c(1,2))
describe(d2$house_income)
hist(d2$house_income, breaks = 10)
boxplot(d2$house_income)
```

### Q.16: Which gender do you identify with?

```{r fig.height=3.5, fig.width=8, echo=FALSE}
par(mfrow=c(1,2))
hist(d2$gender, breaks = 10)
boxplot(d2$gender)
describe(d2$gender)
```


## 2.6 AI treatment/control Questions

### AI 1: Undesirable effects: control_undesirable, treat_undesirable

```{r fig.height=5, fig.width=12, echo=FALSE}
describe(d2$control_undesirable)
describe(d2$treat_undesirable)

par(mfrow=c(2,4))
hist(d2$control_undesirable, breaks = 10)
hist(d2$treat_undesirable, breaks = 10)
boxplot(d2$control_undesirable)
boxplot(d2$treat_undesirable)
```

No statisitcally significant effect of treatment on opinion of undesirable/dangerous effects of AI. However, respondents are 0.19 points less likely to think that there will be undesirable/dangerous effects of AI.

```{r}
t.test(na.omit(d2$control_undesirable), na.omit(d2$treat_undesirable))
wilcox.test(na.omit(d2$control_undesirable), na.omit(d2$treat_undesirable))
```



### AI_2: Jobs: control_jobs, treat_jobs

```{r fig.height=5, fig.width=12, echo=FALSE}
describe(d2$control_jobs)
describe(d2$treat_jobs)

par(mfrow=c(2,4))
hist(d2$control_jobs, breaks = 10)
hist(d2$treat_jobs, breaks = 10)
boxplot(d2$control_jobs)
boxplot(d2$treat_jobs)
```


No statistically significant effect of treatment on opinion of effects of AI on jobs. However, respondents are 0.24 points more likely to think jobs are threatened.

```{r}
t.test(na.omit(d2$control_jobs), na.omit(d2$treat_jobs))
wilcox.test(na.omit(d2$control_jobs), na.omit(d2$treat_jobs))
```

### AI_3: Oversight: control_oversight, treatment_oversight

```{r fig.height=5, fig.width=12, echo=FALSE}
describe(d2$control_oversight)
describe(d2$treat_oversight)

par(mfrow=c(2,4))
hist(d2$control_oversight, breaks = 10)
hist(d2$treat_oversight, breaks = 10)
boxplot(d2$control_oversight)
boxplot(d2$treat_oversight)
```

No statistically significant effect of treatment on opinion of effects of AI oversight. However, treatment effect is -0.3 - people are less likely to think oversight should be required.

```{r}
t.test(na.omit(d2$control_oversight), na.omit(d2$treat_oversight))
wilcox.test(na.omit(d2$control_oversight), na.omit(d2$treat_oversight))
```


### AI_4: Recommender Systems: control_recommender, treat_recommender

```{r fig.height=5, fig.width=12, echo=FALSE}
describe(d2$control_recommender)
describe(d2$treat_recommender)

par(mfrow=c(2,4))
hist(d2$control_recommender, breaks = 10)
hist(d2$treat_recommender, breaks = 10)
boxplot(d2$control_recommender)
boxplot(d2$treat_recommender)
```

No statistically significant effect of treatment on opinion of recommender systems. However, treatment effect is 0.4 - people more likley to accept the opinion of a recommender system over a friend.

```{r}
t.test(na.omit(d2$control_recommender), na.omit(d2$treat_recommender))
wilcox.test(na.omit(d2$control_recommender), na.omit(d2$treat_recommender))
```


### AI_5: Beneficial: control_beneficial, treat_beneficial

```{r fig.height=5, fig.width=12, echo=FALSE}
describe(d2$control_beneficial)
describe(d2$treat_beneficial)

par(mfrow=c(2,4))
hist(d2$control_beneficial, breaks = 10)
hist(d2$treat_beneficial, breaks = 10)
boxplot(d2$control_beneficial)
boxplot(d2$treat_beneficial)
```

No statistically significant effect of treatment on opinion of recommender systems. Treatment effect is very small (-0.07) - people less likley to think that AI will be beneficial to society.

```{r}
t.test(na.omit(d2$control_beneficial), na.omit(d2$treat_beneficial))
wilcox.test(na.omit(d2$control_beneficial), na.omit(d2$treat_beneficial))
```
```{r}
write.csv(d2, "./pilot_cleaned")
```


