---
title: "Exploratory Data Analysis"
author: "Chet Gutwein"
date: "4/8/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r }
library(data.table)
library(dplyr)
library(magrittr)
library(ggplot2)
library(gridExtra)
library(ggExtra)
```

## Read Data

```{r}
d <- fread('./Cleaning_Final_Survey/Cleaned_Full_Survey_dataV1.csv')
```

## Duration

First, we'll take a look at how long participants took to take the survey. 

```{r}
summary(d$duration_seconds)
```

Somehow, we have a partcipant who took 258951 seconds. We set the maximum allowable time on MTurk to 30 minutes, so let's filter out any values above 3600 seconds.
```{r}
d_1 <- d[d$duration_seconds <= 3600]
```

Let's see what the distribution of duration looks like.

```{r}
ggplot(data = d_1) + 
  geom_histogram(mapping = aes(x = duration_seconds), binwidth = 30)
```

## Distribution of Control and Treatment Questions

#### Control Questions

We know for each survey 2 of 5 questions were asked in control, so we should have approximately 400 control questions for each of the 5 categories.

```{r}
keys <- c("undesirable", "jobs", "oversight", "recommender", "beneficial")
control_counts <- c(sum(na.omit(d_1$control_beneficial > 0)), sum(na.omit(d_1$control_jobs > 0)), sum(na.omit(d_1$control_oversight > 0)),sum(na.omit(d_1$control_recommender > 0)),sum(na.omit(d_1$control_beneficial > 0)))
control_data <- data.table(keys, control_counts)
```

```{r}
ggplot(data = control_data) +
  geom_bar(mapping = aes(x = keys, y = control_counts), stat = "identity")
```

#### Treatment Questions

We know for each survey 3 of 5 questions were asked in treatment, so we should have approximately 600 treatment questions for each of the 5 categories.

```{r}
treatment_counts <- c(sum(na.omit(d_1$treat_beneficial > 0)), sum(na.omit(d_1$treat_jobs > 0)), sum(na.omit(d_1$treat_oversight > 0)),sum(na.omit(d_1$treat_recommender > 0)),sum(na.omit(d_1$treat_beneficial > 0)))
treatment_data <- data.table(keys, treatment_counts)
```

```{r}
ggplot(data = treatment_data) +
  geom_bar(mapping = aes(x = keys, y = treatment_counts), stat = "identity")
```

#### Total View

Here's what the total distribution looks like:
```{r}
control_data$type <- 'control'
treatment_data$type <- 'treatment'
```
```{r}
#setnames(control_data, "control_counts","counts")
#setnames(treatment_data, "treatment_counts","counts")
counts_data <- rbind(control_data, treatment_data)
```
```{r}
ggplot(data = counts_data) +
  geom_bar(mapping = aes(x = keys, y = counts, fill = type), stat = "identity")
```
```{r}
ggsave('question_counts.png')
```



## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
