---
title: 'W241: AI Project Final Survey'
subtitle: 'Data Cleaning, EDA, Regression'
author: "Zhaoning Yu"
date: "4/16/2018"
output: pdf_document
---

# Summary: Things done in this Rmd:

- Read data file "Cleaned_Full_Survey_dataV1.csv" into dataframe "d1"

- Create a cleaned version "d2": 

- Adding new variables for attention questions, binary variables for duration

- Adding new variables for measuring subjects' attitude baseline and attitude change after the treatment

- Data analysis I: treatment effect of each individual question

- Data analysis II: treatment is "exposure to 3 balanced paragraphs", within-subject design, measure the change in attitude for each subject

```{r setup, include=FALSE, message=FALSE}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
# knitr::opts_chunk$set(echo = TRUE)

# load packages 
library(Hmisc)              # describe()
library(data.table)
library(foreign)            # ??? what does this package do ????????
library(sandwich)           # vcovHC for robust SE calculation
library(lmtest)             # coeftest 
library(AER)                # ivreg
library(multiwayvcov)       # cluster.vcov()
library(stargazer)          # regression tables
```


# 1. Read Data and Cleaning

## 1.1 Read Data

First read the cleaned full survey data from KH:

```{r}
rm(list=ls())

d1 <- fread('./Cleaned_Full_Survey_dataV1.csv')
head(d1)
```

### 1.2 Create a factor column for attention question 

```{r}
# create indicator vectors to indicate the attention question type
t1 <- 1*!is.na(d1$attention_undesirable) 
t2 <- 2*!is.na(d1$attention_jobs) 
t3 <- 3*!is.na(d1$attention_oversight) 
t4 <- 4*!is.na(d1$attention_recommender) 
t5 <- 5*!is.na(d1$attention_beneficial) 

# add a vector column for attention question
d1$attention_question_code <- t1 + t2 + t3 + t4 + t5
d1$attention_question <- as.factor(t1 + t2 + t3 + t4 + t5)

# rename the levels
levels(d1$attention_question)[levels(d1$attention_question)=="1"] <- "undesirable"
levels(d1$attention_question)[levels(d1$attention_question)=="2"] <- "jobs"
levels(d1$attention_question)[levels(d1$attention_question)=="3"] <- "oversight"
levels(d1$attention_question)[levels(d1$attention_question)=="4"] <- "recommender"
levels(d1$attention_question)[levels(d1$attention_question)=="5"] <- "beneficial"

# levels(d1$attention_question)[levels(d1$attention_question)=="0"] <- "what"
```

## 1.3 Remove some columns and re-arrange:

### Columns that are removed

- "Progress" column has a single value of 100
- "Finished" column has a single value of 1
- "RecordedDate" column has the same information as "EndDate" (+1 second)

### Note:

- "Assignment_##" columns are indicator whether subject assigned to treatment or control for each question
- "Score_##" columns are answers for the question (as control or treatment depending on assignment)

```{r}
d2 <- subset(d1, select=c(ResponseId, mTurkCode, 
                          IPAddress, LocationLatitude, LocationLongitude,
                          StartDate, EndDate, duration_seconds, 
                          gender, education_level, house_income,
                          AI_educated, AI_attitude, learn_anything,
                          assignment_undesirable, assignment_jobs, assignment_oversight, assignment_recommender, assignment_beneficial,
                          score_undesirable, score_jobs, score_oversight, score_recommender, score_beneficial,
                          control_undesirable, control_jobs, control_oversight, control_recommender, control_beneficial,
                          treat_undesirable, treat_jobs, treat_oversight, treat_recommender, treat_beneficial,
                          attention_question_code, attention_question, attention_correct))

# create a categorical variable for duration_seconds
d2$duration = cut(d2$duration_seconds, breaks = c(0, 100, 500, Inf), 
                 labels = c("short", "normal","long"))

# create a binary variable to filter out both short and long survey takers
d2$duration_bin = d2$duration=="normal"

# str(d2)
```

## 1.4 Create variables for gauging subjects' attitude before and after treatment

Note following survey questions:

- Q1 (undesirable): How strongly do you feel that that widespread adoption of AI technology will have dangerous or undesirable consequences? 

- Q2 (jobs): How concerned are you that widespread adoption of Artificial Intelligence will lead to major job losses across several employment sectors? 

- Q3 (oversight): How strongly do you feel that regulatory oversight should be established prior to the widespread adoption of particular AI technologies?

- Q4 (recommender): How likely are you to value a movie recommendation from Netflix over a friend or family member? 

- Q5 (beneficial): How strongly do you feel that widespread adoption of AI technology will be beneficial to society? 

**For Q1 (undesirable), Q2 (jobs), Q3 (oversight: positive change means less favorable attitude towards AI.**

**For Q4 (recommender), Q5(beneficial): positive change means more favorable attitude towards AI.**


```{r}
# STEP1: create an "attitude" variable for each question: 
# (1) range from (-2, -1, 0, 1, 2) based on each individual's answer; 
# (2) positive means more favorable towards AI;

d2$attitude_undesirable <- 3 - d2$score_undesirable
d2$attitude_jobs <- 3 - d2$score_jobs
d2$attitude_oversight <- 3 - d2$score_oversight

d2$attitude_recommender <- d2$score_recommender - 3
d2$attitude_beneficial <- d2$score_beneficial - 3

# STEP2:  create variables for each individual's attidude 
# for the treatment ("AI_attitude_treat") and control ("AI_attitude_control") questions:

# sum of the attitude in 3 treatment questions
d2$AI_attitude_treat <- d2$assignment_undesirable * d2$attitude_undesirable + 
  d2$assignment_jobs * d2$attitude_jobs + d2$assignment_oversight * d2$attitude_oversight + 
  d2$assignment_recommender * d2$attitude_recommender + d2$assignment_beneficial * d2$attitude_beneficial

# sum of the attitude in 2 control questions
d2$AI_attitude_control <- (1-d2$assignment_undesirable) * d2$attitude_undesirable + 
  (1-d2$assignment_jobs) * d2$attitude_jobs + (1-d2$assignment_oversight) * d2$attitude_oversight + 
  (1-d2$assignment_recommender) * d2$attitude_recommender + (1-d2$assignment_beneficial) * d2$attitude_beneficial

# normalize by number of questions to get attitude
d2$AI_attitude_treat <- round(d2$AI_attitude_treat/3, 3)                 # divide by 3 because 3 treatment questions
d2$AI_attitude_control <- round(d2$AI_attitude_control/2, 3)             # divide by 2 because 2 treatment questions

 # difference in attitude between treatment and control questions
d2$AI_attitude_change <- d2$AI_attitude_treat - d2$AI_attitude_control  

# STEP3:  reate a variable for treatment types that each individual get. 

# Since there are 5 questions, each subject get 2 control and 3 treatment questions, 
# there are only (5x4)/(1x2) = 10 possible combinations.

# For example, for the first subject, treatment questions are 1(undesirable), 2(jobs), 4(recommender), 
# so the "treatment_type" is coded "11010"

d2$treatment_type <- ""     # initialize a column with empty strings

# populate the treatment_type column with treatment type code such as "01011" ...

for (i in 1:nrow(d2)) {
  d2[i]$treatment_type = paste(toString(d2[i,"assignment_undesirable"]), 
                               toString(d2[i,"assignment_jobs"]), 
                               toString(d2[i,"assignment_oversight"]),
                               toString(d2[i,"assignment_recommender"]), 
                               toString(d2[i,"assignment_beneficial"]),
                               sep="")
}

```

## 1.5 Write dataframe to csv and check result

```{r}
# write.csv(d2, 'Cleaned_Full_Survey_dataV2.csv', row.names=FALSE)
```

# 2. Data Analysis I: treatment effect of each individual question

In the following regression models, we control for the following and compare different specifications:

- "AI_attitude", "AI_educated": to control for people's attitude toward AI before taking the survey

- "gender", "education_level", "house_income": to control for demographic characteristics

- "learn_anything", "duration_bin": to control for people's attention level for taking the survey


## 2.1 AI_Q1: undesirable

**Q1: How strongly do you feel that that widespread adoption of AI technology will have dangerous or undesirable consequences?**

Treatment of Q1 makes people less concerned about AI, but the difference is small and statistcally insignificant after controlling for other variables.

The effect is bigger for people who originally had more positive feeling toward AI.

```{r fig.height=3.5, fig.width=10, echo=FALSE}
mean(d2[d2$assignment_undesirable==0]$score_undesirable)
mean(d2[d2$assignment_undesirable==1]$score_undesirable)

t.test(d2[d2$assignment_undesirable==0]$score_undesirable, d2[d2$assignment_undesirable==1]$score_undesirable)
wilcox.test(d2[d2$assignment_undesirable==0]$score_undesirable, d2[d2$assignment_undesirable==1]$score_undesirable)

par(mfrow=c(1,3))
hist(d2[d2$assignment_undesirable==0]$score_undesirable)
hist(d2[d2$assignment_undesirable==1]$score_undesirable)
boxplot(score_undesirable ~ assignment_undesirable, data=d2)
```

```{r, warning=FALSE}
m.1.1 <- lm(score_undesirable ~ assignment_undesirable, data=d2)
#coeftest(m.1.1, vcov = vcovHC)

m.1.2 <- lm(score_undesirable ~ assignment_undesirable + AI_attitude + AI_educated, data=d2)
#coeftest(m.1.2, vcov = vcovHC)

m.1.3 <- lm(score_undesirable ~ assignment_undesirable + education_level + house_income + gender, data=d2)
#coeftest(m.1.3, vcov = vcovHC)

m.1.4 <- lm(score_undesirable ~ assignment_undesirable + AI_attitude + AI_educated 
                 + education_level + house_income + gender, data=d2)
#coeftest(m.1.4, vcov = vcovHC)

m.1.5 <- lm(score_undesirable ~ assignment_undesirable + AI_attitude + AI_educated 
                 + education_level + house_income + gender + learn_anything , data=d2)
#coeftest(m.1.5, vcov = vcovHC)

m.1.6 <- lm(score_undesirable ~ assignment_undesirable + AI_attitude + AI_educated 
                 + education_level + house_income + gender + learn_anything + duration_bin, data=d2)
#coeftest(m.1.6, vcov = vcovHC)

se.m.1.1 = sqrt(diag(vcovHC(m.1.1)))
se.m.1.2 = sqrt(diag(vcovHC(m.1.2)))
se.m.1.3 = sqrt(diag(vcovHC(m.1.3)))
se.m.1.4 = sqrt(diag(vcovHC(m.1.4)))
se.m.1.5 = sqrt(diag(vcovHC(m.1.5)))
se.m.1.6 = sqrt(diag(vcovHC(m.1.6)))

stargazer(m.1.1, m.1.2, m.1.3, m.1.4, m.1.5, m.1.6,  type = "text", 
          se = list(se.m.1.1, se.m.1.2, se.m.1.3, se.m.1.4, se.m.1.5, se.m.1.6),
          title = "undesirable",
          omit.stat = c("f", "ser"),
          star.cutoffs = c(0.05,0.01,0.001))
# type = "text"
```

## 2.2 AI_Q2: jobs

**Q2: How concerned are you that widespread adoption of Artificial Intelligence will lead to major job losses across several employment sectors?**

Treatment of Q2 makes people less concerned about AI on jobs, but the difference is small but statistcally significant after controlling for other variables.

The effect is bigger for people who originally had more positive feeling toward AI.

```{r fig.height=3.5, fig.width=10, echo=FALSE}
mean(d2[d2$assignment_jobs==0]$score_jobs)
mean(d2[d2$assignment_jobs==1]$score_jobs)

t.test(d2[d2$assignment_jobs==0]$score_jobs, d2[d2$assignment_jobs==1]$score_jobs)
wilcox.test(d2[d2$assignment_jobs==0]$score_jobs, d2[d2$assignment_jobs==1]$score_jobs)

par(mfrow=c(1,3))
hist(d2[d2$assignment_jobs==0]$score_jobs)
hist(d2[d2$assignment_jobs==1]$score_jobs)
boxplot(score_jobs ~ assignment_jobs, data=d2)
```

```{r, warning=FALSE}
m.2.1 <- lm(score_jobs ~ assignment_jobs, data=d2)

m.2.2 <- lm(score_jobs ~ assignment_jobs + AI_attitude + AI_educated, data=d2)

m.2.3 <- lm(score_jobs ~ assignment_jobs + education_level + house_income + gender, data=d2)

m.2.4 <- lm(score_jobs ~ assignment_jobs + AI_attitude + AI_educated 
                 + education_level + house_income + gender, data=d2)

m.2.5 <- lm(score_jobs ~ assignment_jobs + AI_attitude + AI_educated 
                 + education_level + house_income + gender + learn_anything , data=d2)

m.2.6 <- lm(score_jobs ~ assignment_jobs + AI_attitude + AI_educated 
                 + education_level + house_income + gender + learn_anything + duration_bin, data=d2)

se.m.2.1 = sqrt(diag(vcovHC(m.2.1)))
se.m.2.2 = sqrt(diag(vcovHC(m.2.2)))
se.m.2.3 = sqrt(diag(vcovHC(m.2.3)))
se.m.2.4 = sqrt(diag(vcovHC(m.2.4)))
se.m.2.5 = sqrt(diag(vcovHC(m.2.5)))
se.m.2.6 = sqrt(diag(vcovHC(m.2.6)))

stargazer(m.2.1, m.2.2, m.2.3, m.2.4, m.2.5, m.2.6,  type = "text", 
          se = list(se.m.2.1, se.m.2.2, se.m.2.3, se.m.2.4, se.m.2.5, se.m.2.6),
          title = "jobs",
          omit.stat = c("f", "ser"),
          star.cutoffs = c(0.05,0.01,0.001))
```


## 2.3 AI_Q3: oversight

**Q3: How strongly do you feel that regulatory oversight should be established prior to the widespread adoption of particular AI technologies? **

Treatment and control are not significantly different,  the treatment is higher.

```{r fig.height=3.5, fig.width=10, echo=FALSE}
mean(d2[d2$assignment_oversight==0]$score_oversight)
mean(d2[d2$assignment_oversight==1]$score_oversight)

t.test(d2[d2$assignment_oversight==0]$score_oversight, d2[d2$assignment_oversight==1]$score_oversight)
wilcox.test(d2[d2$assignment_oversight==0]$score_oversight, d2[d2$assignment_oversight==1]$score_oversight)

par(mfrow=c(1,3))
hist(d2[d2$assignment_oversight==0]$score_oversight)
hist(d2[d2$assignment_oversight==1]$score_oversight)
boxplot(score_oversight ~ assignment_oversight, data=d2)
```


```{r, warning=FALSE}
m.3.1 <- lm(score_oversight ~ assignment_oversight, data=d2)

m.3.2 <- lm(score_oversight ~ assignment_oversight + AI_attitude + AI_educated, data=d2)

m.3.3 <- lm(score_oversight ~ assignment_oversight + education_level + house_income + gender, data=d2)

m.3.4 <- lm(score_oversight ~ assignment_oversight + AI_attitude + AI_educated 
                 + education_level + house_income + gender, data=d2)

m.3.5 <- lm(score_oversight ~ assignment_oversight + AI_attitude + AI_educated 
                 + education_level + house_income + gender + learn_anything , data=d2)

m.3.6 <- lm(score_oversight ~ assignment_oversight + AI_attitude + AI_educated 
                 + education_level + house_income + gender + learn_anything + duration_bin, data=d2)

se.m.3.1 = sqrt(diag(vcovHC(m.3.1)))
se.m.3.2 = sqrt(diag(vcovHC(m.3.2)))
se.m.3.3 = sqrt(diag(vcovHC(m.3.3)))
se.m.3.4 = sqrt(diag(vcovHC(m.3.4)))
se.m.3.5 = sqrt(diag(vcovHC(m.3.5)))
se.m.3.6 = sqrt(diag(vcovHC(m.3.6)))

stargazer(m.3.1, m.3.2, m.3.3, m.3.4, m.3.5, m.3.6, type = "text", 
          se = list(se.m.3.1, se.m.3.2, se.m.3.3, se.m.3.4, se.m.3.5, se.m.3.6),
          title = "oversight",
          omit.stat = c("f", "ser"),
          star.cutoffs = c(0.05,0.01,0.001))
```


## 2.4 AI_Q4: recommender

**Q4: How likely are you to value a movie recommendation from Netflix over a friend or family member?**

Treatment and control are not significantly different, the treatment is lower.

```{r fig.height=3.5, fig.width=10, echo=FALSE}
mean(d2[d2$assignment_recommender==0]$score_recommender)
mean(d2[d2$assignment_recommender==1]$score_recommender)

t.test(d2[d2$assignment_recommender==0]$score_recommender, d2[d2$assignment_recommender==1]$score_recommender)
wilcox.test(d2[d2$assignment_recommender==0]$score_recommender, d2[d2$assignment_recommender==1]$score_recommender)

par(mfrow=c(1,3))
hist(d2[d2$assignment_recommender==0]$score_recommender)
hist(d2[d2$assignment_recommender==1]$score_recommender)
boxplot(score_recommender ~ assignment_recommender, data=d2)
```

```{r, warning=FALSE}
m.4.1 <- lm(score_recommender ~ assignment_recommender, data=d2)

m.4.2 <- lm(score_recommender ~ assignment_recommender + AI_attitude + AI_educated, data=d2)

m.4.3 <- lm(score_recommender ~ assignment_recommender + education_level + house_income + gender, data=d2)

m.4.4 <- lm(score_recommender ~ assignment_recommender + AI_attitude + AI_educated 
                 + education_level + house_income + gender, data=d2)

m.4.5 <- lm(score_recommender ~ assignment_recommender + AI_attitude + AI_educated 
                 + education_level + house_income + gender + learn_anything , data=d2)

m.4.6 <- lm(score_recommender ~ assignment_recommender + AI_attitude + AI_educated 
                 + education_level + house_income + gender + learn_anything + duration_bin, data=d2)

se.m.4.1 = sqrt(diag(vcovHC(m.4.1)))
se.m.4.2 = sqrt(diag(vcovHC(m.4.2)))
se.m.4.3 = sqrt(diag(vcovHC(m.4.3)))
se.m.4.4 = sqrt(diag(vcovHC(m.4.4)))
se.m.4.5 = sqrt(diag(vcovHC(m.4.5)))
se.m.4.6 = sqrt(diag(vcovHC(m.4.6)))

stargazer(m.4.1, m.4.2, m.4.3, m.4.4, m.4.5, m.4.6,  type = "text", 
          se = list(se.m.4.1, se.m.4.2, se.m.4.3, se.m.4.4, se.m.4.5, se.m.4.6),
          title = "recommender",
          omit.stat = c("f", "ser"),
          star.cutoffs = c(0.05,0.01,0.001))
```

## 2.5 AI_Q5: beneficial

**Q5: How strongly do you feel that widespread adoption of AI technology will be beneficial to society?**

Treatment and control are not significantly different, the treatment is lower.

```{r fig.height=3.5, fig.width=10, echo=FALSE}
mean(d2[d2$assignment_beneficial==0]$score_beneficial)
mean(d2[d2$assignment_beneficial==1]$score_beneficial)

t.test(d2[d2$assignment_beneficial==0]$score_beneficial, d2[d2$assignment_beneficial==1]$score_beneficial)
wilcox.test(d2[d2$assignment_beneficial==0]$score_beneficial, d2[d2$assignment_beneficial==1]$score_beneficial)

par(mfrow=c(1,3))
hist(d2[d2$assignment_beneficial==0]$score_beneficial)
hist(d2[d2$assignment_beneficial==1]$score_beneficial)
boxplot(score_beneficial ~ assignment_beneficial, data=d2)
```

```{r, warning=FALSE}
m.5.1 <- lm(score_beneficial ~ assignment_beneficial, data=d2)

m.5.2 <- lm(score_beneficial ~ assignment_beneficial + AI_attitude + AI_educated, data=d2)

m.5.3 <- lm(score_beneficial ~ assignment_beneficial + education_level + house_income + gender, data=d2)

m.5.4 <- lm(score_beneficial ~ assignment_beneficial + AI_attitude + AI_educated 
                 + education_level + house_income + gender, data=d2)

m.5.5 <- lm(score_beneficial ~ assignment_beneficial + AI_attitude + AI_educated 
                 + education_level + house_income + gender + learn_anything , data=d2)

m.5.6 <- lm(score_beneficial ~ assignment_beneficial + AI_attitude + AI_educated 
                 + education_level + house_income + gender + learn_anything + duration_bin , data=d2)

se.m.5.1 = sqrt(diag(vcovHC(m.5.1)))
se.m.5.2 = sqrt(diag(vcovHC(m.5.2)))
se.m.5.3 = sqrt(diag(vcovHC(m.5.3)))
se.m.5.4 = sqrt(diag(vcovHC(m.5.4)))
se.m.5.5 = sqrt(diag(vcovHC(m.5.5)))
se.m.5.6 = sqrt(diag(vcovHC(m.5.6)))

stargazer(m.5.1, m.5.2, m.5.3, m.5.4, m.5.5, m.5.6,   type = "text", 
          se = list(se.m.5.1, se.m.5.2, se.m.5.3, se.m.5.4, se.m.5.5, se.m.5.6),
          title = "beneficial",
          omit.stat = c("f", "ser"),
          star.cutoffs = c(0.05,0.01,0.001))
```


# 3. Data Analysis II: effect of 3 questions on each subject's attitude 

Also for each treatment type, ~100 subjects, the assignment is balanced.

```{r}
table(d2$treatment_type)
```

#### Explanation of the "treatment_type" 

For example,  code "00111" means the subject got control versions for questions 1 (undesirable) 2(jobs), and treatment versions for questions 3 (oversight), 4 (recommender), 5 (beneficial).

## 3.1 EDA 

### 3.1.1 Means 

Mean of "AI_attitude_control" is -0.2778 and is significantly different from 0 with p-value = 2.2e-16.

Mean of "AI_attitude_treat" is -0.2691 and is significantly different from 0 with p-value = 2.2e-16.

Mean of "AI_attitude_change" is 0.0087 but is not significantly with p-value = 0.7618.

```{r fig.height=3.5, fig.width=10, echo=FALSE}
t.test(d2$AI_attitude_control)
t.test(d2$AI_attitude_treat)
t.test(d2$AI_attitude_change)

par(mfrow=c(1,3))
hist(d2$AI_attitude_control, breaks=12, main="AI_attitude_control", col = "yellow")
hist(d2$AI_attitude_treat, breaks=12, main="AI_attitude_treat", col= "green")
hist(d2$AI_attitude_change, breaks=20, main="AI_attitude_change", col = "blue")
```

### 3.1.2 Interesting dependencies:

- No difference in attitude change between male and female.

- People who are more educated seem to become more positive toward AI after taking the survey. 

- Less educated people (assuming "other" are less educated) become more negative toward AI after taking the survey.

```{r fig.height=3.5, fig.width=10, echo=FALSE}
par(mfrow=c(1,3))

boxplot(AI_attitude_change ~ gender, data=d2, main="gender")
abline(h=0, col='red')

boxplot(AI_attitude_change ~ education_level, data=d2, main="education level")
abline(h=0, col='red')

boxplot(AI_attitude_change ~ house_income, data=d2, main="household income")
abline(h=0, col='red')
```

People who were originally educated about AI seem to become less favorable toward AI after taking the survey:

- People who were originally positive towards AI become less positive toward AI after taking the survey.

- People who were originally negative towards AI become more positive toward AI after taking the survey.

```{r fig.height=3.5, fig.width=10, echo=FALSE}
par(mfrow=c(1,2))

boxplot(AI_attitude_change ~ AI_educated, data=d2, main="AI educated")
abline(h=0, col='red')

boxplot(AI_attitude_change ~ AI_attitude, data=d2, main = '"AI_attitude_change" vs "AI_attitude"')
abline(h=0, col='red')
```

- People's attitude change strong depends on "treatment_type" (what treatment questions they get) - this is the "fixed effects" we want to control.

```{r fig.height=4, fig.width=10, echo=FALSE}
boxplot(AI_attitude_change ~ treatment_type, data=d2, main="AI attitude change vs. treatment type")
abline(h=0, col='red')
```

```{r fig.height=3.5, fig.width=10, echo=FALSE}
#cor(d2$AI_attitude, d2$AI_attitude_control)         # NA
#cor(d2$AI_attitude_treat, d2$AI_attitude_control)   # 0.3721

par(mfrow=c(1,2))
boxplot(AI_attitude_treat~AI_attitude_control, data=d2, xlab="AI_attitude_control", ylab="AI_attitude_treat")
boxplot(AI_attitude ~ AI_attitude_control, data=d2, xlab="AI_attitude_control", ylab="AI_attitude")
```

```{r fig.height=3.5, fig.width=10, echo=FALSE}
par(mfrow=c(1,2))
boxplot(AI_attitude_change ~ AI_attitude_control, data=d2, xlab="AI_attitude_control", ylab="AI_attitude_change")
boxplot(AI_attitude_change ~ AI_attitude_treat, data=d2, xlab="AI_attitude_treat", ylab="AI_attitude_change")
```

## Comment:

The dependence on "AI_attitude_control" and "AI_attitude_treat" should be expected, because AI_attitude_change is defined as $AI\_attitude\_change = AI\_attitude_treat-AI\_attitude\_control$.


## 3.2 Regression

### 3.2.1 Regression I

```{r, warning=FALSE}

# d2$AI_attitude <- d2$AI_attitude -3

# models without controlling for "treatment_type" fixed effects

m.6.1 <- lm(AI_attitude_change ~ AI_attitude, data=d2)

m.6.2 <- lm(AI_attitude_change ~ AI_attitude + AI_educated, data=d2)

m.6.3 <- lm(AI_attitude_change ~ education_level + house_income + gender, data=d2)

m.6.4 <- lm(AI_attitude_change ~ AI_attitude + AI_educated 
                 + education_level + house_income + gender, data=d2)

m.6.5 <- lm(AI_attitude_change ~ AI_attitude + AI_educated 
                 + education_level + house_income + gender + learn_anything , data=d2)

m.6.6 <- lm(AI_attitude_change ~ AI_attitude + AI_educated 
                 + education_level + house_income + gender + learn_anything + duration_bin, data=d2)

m.6.7 <- lm(AI_attitude_change ~ AI_attitude + AI_educated 
                 + education_level + house_income + gender + learn_anything + duration_bin + attention_correct, data=d2)

# models with controlling for "treatment_type" fixed effects

m.6.8 <- lm(AI_attitude_change ~ AI_attitude + treatment_type, data=d2)

m.6.9 <- lm(AI_attitude_change ~ AI_attitude + AI_educated + treatment_type, data=d2)

m.6.10 <- lm(AI_attitude_change ~ education_level + house_income + gender + treatment_type, data=d2)

m.6.11 <- lm(AI_attitude_change ~ AI_attitude + AI_educated 
                 + education_level + house_income + gender + treatment_type, data=d2)

m.6.12 <- lm(AI_attitude_change ~ AI_attitude + AI_educated 
                 + education_level + house_income + gender + learn_anything + treatment_type , data=d2)

m.6.13 <- lm(AI_attitude_change ~ AI_attitude + AI_educated 
                 + education_level + house_income + gender + learn_anything + duration_bin + treatment_type, data=d2)

m.6.14 <- lm(AI_attitude_change ~ AI_attitude + AI_educated 
                 + education_level + house_income + gender + learn_anything + duration_bin + attention_correct + treatment_type, data=d2)


se.m.6.1 = sqrt(diag(vcovHC(m.6.1)))
se.m.6.2 = sqrt(diag(vcovHC(m.6.2)))
se.m.6.3 = sqrt(diag(vcovHC(m.6.3)))
se.m.6.4 = sqrt(diag(vcovHC(m.6.4)))
se.m.6.5 = sqrt(diag(vcovHC(m.6.5)))
se.m.6.6 = sqrt(diag(vcovHC(m.6.6)))
se.m.6.7 = sqrt(diag(vcovHC(m.6.7)))
se.m.6.8 = sqrt(diag(vcovHC(m.6.8)))
se.m.6.9 = sqrt(diag(vcovHC(m.6.9)))
se.m.6.10 = sqrt(diag(vcovHC(m.6.10)))
se.m.6.11 = sqrt(diag(vcovHC(m.6.11)))
se.m.6.12 = sqrt(diag(vcovHC(m.6.12)))
se.m.6.13 = sqrt(diag(vcovHC(m.6.13)))
se.m.6.14 = sqrt(diag(vcovHC(m.6.14)))


stargazer(m.6.1, m.6.2, m.6.3, m.6.4, m.6.5, m.6.6, m.6.7, m.6.8, m.6.9, m.6.10, m.6.11, m.6.12, m.6.13, m.6.14,
          type = "text", 
          se = list(se.m.6.1, se.m.6.2, se.m.6.3, se.m.6.4, se.m.6.5, se.m.6.6, se.m.6.7, 
                    se.m.6.8, se.m.6.9, se.m.6.10, se.m.6.11, se.m.6.12, se.m.6.13, se.m.6.14),
          title = "AI attitude change",
          omit.stat = c("f", "ser"),
          star.cutoffs = c(0.05,0.01,0.001))
```




```{r}
plot(m.6.14)
```

## generate a table for the paper

```{r, warning=FALSE}
stargazer(m.6.8, m.6.9, m.6.11, m.6.12, m.6.13, m.6.14,
          type = "text", 
          se = list(se.m.6.8, se.m.6.9, se.m.6.11, se.m.6.12, se.m.6.13, se.m.6.14),
          title = "AI attitude change",
          omit.stat = c("f", "ser"),
          star.cutoffs = c(0.05,0.01,0.001))
```



# 4. Regression II

- Due to the definiation of "AI_attitude_change = AI_attitude_treat - AI_attitude_control", adding both "AI_attitude_control" and "AI_attitude_treat" to the specification will totally absorb the effect and yield coefficients -1 and 1 for these two variables. 

- The following regression may not be sensible, because "AI_attitude_change" is defined by "AI_attitude_treat - AI_attitude_control", so the large negative coefficient for "AI_attitude_control" and the large positive coefficient for "AI_attitude_treat" should be expected.

```{r}
m.7.1 <- lm(AI_attitude_change ~  AI_attitude_control,  data=d2)

m.7.2 <- lm(AI_attitude_change ~  AI_attitude_control + AI_attitude, data=d2)

m.7.3 <- lm(AI_attitude_change ~  AI_attitude_control + AI_attitude + AI_educated, data=d2)

m.7.4 <- lm(AI_attitude_change ~  AI_attitude_control + AI_attitude + AI_educated +
              + education_level + house_income + gender + learn_anything + duration_bin + attention_correct, data=d2)

m.7.5 <- lm(AI_attitude_change ~  AI_attitude_control + AI_attitude + AI_educated +
              + education_level + house_income + gender + learn_anything + duration_bin + attention_correct + treatment_type, data=d2)

m.7.6 <- lm(AI_attitude_change ~  AI_attitude_control + AI_attitude_treat + AI_attitude + AI_educated +
              + education_level + house_income + gender + learn_anything + duration_bin + attention_correct + treatment_type, data=d2)

se.m.7.1 = sqrt(diag(vcovHC(m.7.1)))
se.m.7.2 = sqrt(diag(vcovHC(m.7.2)))
se.m.7.3 = sqrt(diag(vcovHC(m.7.3)))
se.m.7.4 = sqrt(diag(vcovHC(m.7.4)))
se.m.7.5 = sqrt(diag(vcovHC(m.7.5)))
se.m.7.6 = sqrt(diag(vcovHC(m.7.6)))

stargazer(m.7.1, m.7.2, m.7.3, m.7.4, m.7.5, m.7.6,
          type = "text", 
          se = list(se.m.7.1, se.m.7.2, se.m.7.3, se.m.7.4, se.m.7.5, se.m.7.6),
          title = "AI attitude change",
          omit.stat = c("f", "ser"),
          star.cutoffs = c(0.05,0.01,0.001))

```

```{r}
plot(m.7.5)
```
```{r}
table(d2$AI_attitude)
hist(d2$AI_attitude)
```

