---
title: "Pilot 2 - Exploratory Data Analysis"
author: "Chet Gutwein"
date: "4/9/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r }
library(data.table)
library(dplyr)
library(magrittr)
library(ggplot2)
library(gridExtra)
library(ggExtra)
```

## Read Data

```{r}
d <- fread('./Cleaned_Pilot2.csv')
```

## Duration

First, we'll take a look at how long participants took to take the survey. 

```{r}
summary(d$duration_seconds)
```

Let's see what the distribution of duration looks like.

```{r}
ggplot(data = d) + 
  geom_histogram(mapping = aes(x = duration_seconds), binwidth = 60)
```

## Distribution of Control and Treatment Questions

#### Control Questions

We know for each survey 2 of 5 questions were asked in control, so we should have approximately 12 control questions for each of the 5 categories.

```{r}
keys <- c("undesirable", "jobs", "oversight", "recommender", "beneficial")
control_counts <- c(sum(na.omit(d$control_beneficial > 0)), sum(na.omit(d$control_jobs > 0)), sum(na.omit(d$control_oversight > 0)),sum(na.omit(d$control_recommender > 0)),sum(na.omit(d$control_beneficial > 0)))
control_data <- data.table(keys, control_counts)
```

```{r}
ggplot(data = control_data) +
  geom_bar(mapping = aes(x = keys, y = control_counts), stat = "identity")
```

#### Treatment Questions

We know for each survey 3 of 5 questions were asked in treatment, so we should have approximately 18 treatment questions for each of the 5 categories.

```{r}
treatment_counts <- c(sum(na.omit(d$treat_beneficial > 0)), sum(na.omit(d$treat_jobs > 0)), sum(na.omit(d$treat_oversight > 0)),sum(na.omit(d$treat_recommender > 0)),sum(na.omit(d$treat_beneficial > 0)))
treatment_data <- data.table(keys, treatment_counts)
```

```{r}
ggplot(data = treatment_data) +
  geom_bar(mapping = aes(x = keys, y = treatment_counts), stat = "identity")
```

#### Total View

Here's what the total distribution looks like:
```{r}
control_data$type <- 'control'
treatment_data$type <- 'treatment'
```
```{r}
setnames(control_data, "control_counts","counts")
setnames(treatment_data, "treatment_counts","counts")
counts_data <- rbind(control_data, treatment_data)
```
```{r}
ggplot(data = counts_data) +
  geom_bar(mapping = aes(x = keys, y = counts, fill = type), stat = "identity")
```
```{r}
ggsave('question_counts_pilot_2.png')
```

## Location of Participants

Participants should be located in the United States, and hopefully have a distribution across the country that looks reasonably random.

```{r}
# more libraries for maps
library(ggmap)
library(maps)
library(mapdata)
```
```{r}
usa <- map_data("usa")
ggplot() + geom_polygon(data = usa, aes(x=long, y = lat, group = group)) + 
  coord_fixed(1.3) + geom_point(data = d, aes(x = LocationLongitude, y = LocationLatitude), color = "violet", size = 3) +  geom_point(data = d, aes(x = LocationLongitude, y = LocationLatitude), color = "yellow", size = 2)
```
```{r}
ggsave('usa_map_pilot_2.png')
```

## Control and Treatment

Let's take a look at how the ratings for each of the 5 questions stack up in treatment vs. control. To visualize this, we'll superimpose a density plot of the score responses for each. Density plots might look a little strange because it's a pilot and we only have a total of 30 responses, but this should be a pretty usefully view for the experimental results. 

```{r}
d$assignment_oversight <- as.factor(d$assignment_oversight)
g1 <- d %>%
    ggplot(aes(x = score_oversight, fill = assignment_oversight)) +
    geom_density(alpha = 0.7) +
    scale_fill_manual(values = c('darkblue', 'grey')) + 
    labs(x = 'Score', y = '', title = 'Does AI require regulatory oversight?')

d$assignment_beneficial <- as.factor(d$assignment_beneficial)
g2 <- d %>%
    ggplot(aes(x = score_beneficial, fill = assignment_beneficial)) +
    geom_density(alpha = 0.7) +
    scale_fill_manual(values = c('darkblue', 'grey')) + 
    labs(x = 'Score', y = '', title = 'Will AI prove beneficial to society?')

d$assignment_undesirable <- as.factor(d$assignment_undesirable)
g3 <- d %>%
    ggplot(aes(x = score_undesirable, fill = assignment_undesirable)) +
    geom_density(alpha = 0.7) +
    scale_fill_manual(values = c('darkblue', 'grey')) + 
    labs(x = 'Score', y = '', title = 'Will AI have undesirable consequences?')

d$assignment_jobs <- as.factor(d$assignment_jobs)
g4 <- d %>%
    ggplot(aes(x = score_jobs, fill = assignment_jobs)) +
    geom_density(alpha = 0.7) +
    scale_fill_manual(values = c('darkblue', 'grey')) + 
    labs(x = 'Score', y = '', title = 'Will AI threaten your job security?')

d$assignment_recommender <- as.factor(d$assignment_recommender)
g5 <- d %>%
    ggplot(aes(x = score_recommender, fill = assignment_recommender)) +
    geom_density(alpha = 0.7) +
    scale_fill_manual(values = c('darkblue', 'grey')) + 
    labs(x = 'Score', y = '', title = 'Do you favor recommender system over a friend?')
```

Duration of Survey Time vs. Correct Response to attention question

```{r}
d$attention_correct <- as.factor(d$attention_correct)
g6 <- d %>%
    ggplot(aes(x = duration_seconds, fill = attention_correct)) +
    geom_density(alpha = 0.7) +
    scale_fill_manual(values = c('darkblue', 'grey')) + 
    labs(x = 'Duration of survey (sec)', y = '', title = 'Duration of Survey')
```

```{r}
attention_percentages <- c(mean(d$attention_correct[d$attention_question_code == 1]), mean(d$attention_correct[d$attention_question_code == 2]), mean(d$attention_correct[d$attention_question_code == 3]), 1 - mean(d$attention_correct[d$attention_question_code == 4]), mean(d$attention_correct[d$attention_question_code == 5]))
keys <- c("undesirable", "jobs", "oversight", "recommender", "beneficial")
attention_table <- data.table(keys, attention_percentages)
```
```{r}
g8 <- ggplot(data = attention_table) +
  geom_bar(mapping = aes(x = keys, y = attention_percentages), fill = 'darkblue', stat = "identity") + coord_flip()
mean(d$attention_correct)
ggsave('attention_q_2.png')
```

Checking some things by re-loading the raw data.
```{r}
d_raw <- fread('Pilot2_Expert_mTurk_04_05_2018.csv')
```
```{r}
d$attention_correct[d$attention_question_code == 4] <- 1 - d$attention_correct[d$attention_question_code == 4]
```

## Treatment Effect Analysis
```{r}
df <- d
```

### AI 1: Undesirable effects: control_undesirable, treat_undesirable

```{r fig.height=5, fig.width=12, echo=FALSE}
library(Hmisc) 
describe(df$control_undesirable)
describe(df$treat_undesirable)

par(mfrow=c(2,4))
hist(df$control_undesirable, breaks = 10)
hist(df$treat_undesirable, breaks = 10)
boxplot(df$control_undesirable)
boxplot(df$treat_undesirable)
```

$$
ATE_{undesirable} = 2.833 - 2.9 = -0.067
$$

Another way to interpret the result is to run a linear regression and take into consideration some fixed effects and/or covariates. In our survey, one of the preliminary questions asked participants  

"How do you feel in general towards artificial intelligence?"   

```{r}
ggplot(data = d) + 
  geom_histogram(mapping = aes(x = AI_attitude), bins = 5, fill = 'darkblue', col='gray')
```

We have taken this variable into consideration along with the treatment and run a regression using the form:
$$
Score_{undesirable} = \alpha + \beta_{treat}*Treatment + \beta_{attitude}*Attitude + \epsilon
$$
```{r}
lm_1 <- lm(score_undesirable ~ assignment_undesirable + AI_attitude, data=d)
```
```{r}
summary(lm_1)
```

Here, we can see that there is a slightly stronger treatment effect, however, none of these are significant. We wouldn't expect significant results from a pilot study of 30 subjects anyway.

### AI 2: jobs: control_jobs, treat_jobs

```{r fig.height=5, fig.width=12, echo=FALSE}
describe(df$control_jobs)
describe(df$treat_jobs)
```

$$
ATE_{jobs} = 2.714 - 3.714 = -1.0
$$

```{r}
lm_2 <- lm(score_jobs ~ assignment_jobs + AI_attitude, data=d)
summary(lm_2)
```


### AI 3: Oversight: control_oversight, treat_oversight

```{r}
describe(df$control_oversight)
describe(df$treat_oversight)
```

$$
ATE_{oversight} = 4.222 - 3.9 = 0.322
$$

```{r}
lm_3 <- lm(score_oversight ~ assignment_oversight + AI_attitude, data=d)
summary(lm_3)
```

### AI 4: Recommender Systems: control_recommender, treat_recommender

```{r echo=FALSE}
describe(df$control_recommender)
describe(df$treat_recommender)
```

$$
ATE_{recommender} = 2.333 - 2.9 = -0.567
$$

```{r}
lm_4 <- lm(score_recommender ~ assignment_recommender + AI_attitude, data=d)
summary(lm_4)
```

### AI 5: Beneficial

```{r echo=FALSE}
describe(df$control_beneficial)
describe(df$treat_beneficial)
```

$$
ATE_{beneficial} = 2.75 - 3.083 = -0.323
$$

```{r}
lm_5 <- lm(score_beneficial ~ assignment_beneficial + AI_attitude, data=d)
summary(lm_5)
```


## Covariates

We surveyed participants for the following information to include as covariates:
 * Education level in relation to AI (Scale from 1 to 5)
 * Annual Household Income
 * Highest Education Completed
 * Gender
 * Did you learn anything from taking this survey?

```{r}
cov_1 <- ggplot(data = d) + 
  geom_histogram(mapping = aes(x = AI_educated), bins = 5, fill = 'darkblue', col='gray')

cov_2 <- ggplot(data = d) + 
  geom_histogram(mapping = aes(x = house_income), bins = 4, fill = 'darkblue', col='gray')

cov_3 <- ggplot(data = d) + 
  geom_histogram(mapping = aes(x = education_level), bins = 4, fill = 'darkblue', col='gray')

cov_4 <- ggplot(data = d) + 
  geom_histogram(mapping = aes(x = gender), bins = 2, fill = 'darkblue', col='gray')

cov_5 <- ggplot(data = d) + 
  geom_histogram(mapping = aes(x = learn_anything), bins = 2, fill = 'darkblue', col='gray')
```

```{r}
cov_1
cov_2
cov_3
cov_4
cov_5
```

