---
title: "AI - Simulation, Power Estimate"
author: "Chet Gutwein"
date: "March 27, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# W241 - Artificial Intelligence Final Project
  
## Investigation into Statistical Power for prior to survey launch

## Making some assumptions in order to carry out simulation

 1.) Even distribution of total response for each question with variance of 1.2
 2.) Estimating effect size between 0.1 and 0.3
 3.) Targeting 1,000 subjects: 500 control, 500 treatment for each question (in our experiment this is really going to be 400 control and 600 treatment - but easier to do the simulation with an even split)
 4.) outcome variable is a score on a diverging scale from 1 to 5, with 3 being neutral.
 
```{r}
#Defining variables
n_total <- 1000
sigma2 <- 1.2
```

Defining control values for 1000 subjects.

```{r}
#Default control values
po.control <- round(rnorm(n_total, 3, sigma2))
po.control[po.control < 1] = 1
#sum(po.control > 5)
po.control[po.control > 5] = 5
po.control <- abs(3-po.control) # normalizing here for distance from 3/neutral
hist(po.control,3)
mean(po.control)
var(po.control)
```

Defining hypothetical treatment values for 1000 subjects.

```{r}
#Default treatment values
t_1 <- -0.2
po.treatment <- round(rnorm(n_total, mean(po.control) + t_1, var(po.control)))
sum(po.treatment > 2)
sum(po.treatment < 0)
po.treatment[po.treatment < 0] = 0
po.treatment[po.treatment > 2] = 2
hist(po.treatment,3)
mean(po.treatment)
var(po.treatment)
```

```{r}
#Randomize control and treatment vector
randomize <- function() sample(c(rep(0,500), rep(1, 500)))
est.ate <- function(outcome, treat) mean(outcome[treat==1]) - mean(outcome[treat==0]) 
```

```{r}
treatment <- randomize()
outcomes <- po.treatment * treatment + po.control*(1-treatment) 
ate <- est.ate(outcomes, treatment)

est.ate(outcomes, randomize())
est.ate(outcomes, randomize())
est.ate(outcomes, randomize())

distribution_01 <- replicate(5000, est.ate(outcomes, randomize())) 
plot(density(distribution_01))
abline(v=ate)
mean(ate <= distribution_01)
```

```{r}
simulate.study <- function(t_1){ 
  po.control <- round(rnorm(1000, 3, 1.2))
  po.control[po.control < 1] = 1
  po.control[po.control > 5] = 5
  po.control <- abs(3-po.control) 
  po.treatment <- round(rnorm(1000, mean(po.control) + t_1, var(po.control)))
  po.treatment[po.treatment < 0] = 0
  po.treatment[po.treatment > 2] = 2 
  treatment <- randomize() 
  outcomes <-  po.treatment * treatment + po.control * (1-treatment) 
  ate <- est.ate(outcomes, treatment) 
  distribution.under.sharp.null <- replicate(1000, est.ate(outcomes, randomize())) 
  return(mean(ate > distribution.under.sharp.null)) 
} 
```

## Getting Power for different ATE values

```{r}
pvals_0 <- replicate(1000, simulate.study(0))
plot(density(pvals_0)) 
mean(pvals_0 < 0.05)
```

```{r}
pvals_1 <- replicate(1000, simulate.study(-0.1))
plot(density(pvals_1)) 
mean(pvals_1 < 0.05)
```

```{r}
pvals_2 <- replicate(1000, simulate.study(-0.2))
plot(density(pvals_2)) 
mean(pvals_2 < 0.05)
```


