---
title: "Cleaning Final Survey Data"
author: "Kiersten Henderson"
date: "4/5/2018"
output: pdf_document
---

```{r setup, include=FALSE, message=FALSE}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
# knitr::opts_chunk$set(echo = TRUE)

# load packages 
library(Hmisc)              
library(data.table)
library(foreign)           
library(sandwich)           
library(lmtest)            
library(AER)               
library(multiwayvcov)       
```

# 1. Read Data

## 1.1 Read Data

```{r}
d1 <- fread('Filtered_Raw_Survey_data_04_05_2018.csv')
head(d1)
#View(d1)
```


## 1.2 Remove useless rows and columns

```{r}
# Save the column names
header <- d1[1,]                             # save the header information

# Remove useless rows
d2 <- d1[-c(1,2)]                           # remove rows 1, 2 (redundent headers)

# Remove useless columns
d2 <- subset(d2, select = -c(RecipientLastName, RecipientFirstName, RecipientEmail, ExternalReference))  # empty columns
d2 <- subset(d2, select = -c(Status, DistributionChannel, UserLanguage))        # columns with the same value for all
head(d2)
```


## 1.3 Ensure correct data types

Note everything is a string in this data frame:

```{r, message=FALSE}
str(d2)
```

Change strings into numeric values:

```{r}
# Turn following columns from string to numeric
d2[, 'Progress'] <- sapply(d2[, 'Progress'], as.numeric)
d2[, 'Duration..in.seconds.'] <- sapply(d2[, 'Duration..in.seconds.'], as.numeric)
d2[, 'LocationLatitude'] <- sapply(d2[, 'LocationLatitude'], as.numeric)
d2[, 'LocationLongitude'] <- sapply(d2[, 'LocationLongitude'], as.numeric)
d2[, 'mTurkCode'] <- sapply(d2[, 'mTurkCode'], as.numeric)

d2[, 'Q1_1'] <- sapply(d2[, 'Q1_1'], as.numeric)
d2[, 'Q3_1'] <- sapply(d2[, 'Q3_1'], as.numeric)
d2[, 'Q6_1'] <- sapply(d2[, 'Q6_1'], as.numeric)
d2[, 'Q8_1'] <- sapply(d2[, 'Q8_1'], as.numeric)
d2[, 'Q10_1'] <- sapply(d2[, 'Q10_1'], as.numeric)
d2[, 'Q12_1'] <- sapply(d2[, 'Q12_1'], as.numeric)
d2[, 'Q20_1'] <- sapply(d2[, 'Q20_1'], as.numeric)
d2[, 'Q5_1'] <- sapply(d2[, 'Q5_1'], as.numeric)
d2[, 'Q7_1'] <- sapply(d2[, 'Q7_1'], as.numeric)
d2[, 'Q9_1'] <- sapply(d2[, 'Q9_1'], as.numeric)
d2[, 'Q11_1'] <- sapply(d2[, 'Q11_1'], as.numeric)
d2[, 'Q13_1'] <- sapply(d2[, 'Q13_1'], as.numeric)
d2[, 'Q33_1'] <- sapply(d2[, 'Q33_1'], as.numeric)
d2[, 'Q34_1'] <- sapply(d2[, 'Q34_1'], as.numeric)
d2[, 'Q35_1'] <- sapply(d2[, 'Q35_1'], as.numeric)
d2[, 'Q36_1'] <- sapply(d2[, 'Q36_1'], as.numeric)
d2[, 'Q37_1'] <- sapply(d2[, 'Q37_1'], as.numeric)

# Turn 'TRUE' 'FALSE' to 1 and 0
f1 <- function(x) {
  if (x=='True') {
    return(1)
  } else if (x=='False') {
    return(0)
  } else {
    return(NA)
  }
}

d2$Q18 <- sapply(d2$Q18, f1)
d2$Q19 <- sapply(d2$Q19, f1)
d2$Q23 <- sapply(d2$Q23, f1)
d2$Q17 <- sapply(d2$Q17, f1)
d2$Q24 <- sapply(d2$Q24, f1)
d2$Finished <- sapply(d2$Finished, f1)

# Turn 'Yes' 'No' to 1 and 0
f2 <- function(x) {
  if (x=='Yes') {
    return(1)
  } else if (x=='No') {
    return(0)
  } else {
    return(NA)
  }
}

d2$Q31 <- sapply(d2$Q31, f2)

# Turn 'Male' 'Female' to 1 and 0
f3 <- function(x) {
  if (x=='Male') {
    return(1)
  } else if (x=='Female') {
    return(0)
  } else {
    return(NA)
  }
}

d2$Q16 <- sapply(d2$Q16, f3)

# Education into 0, 1, 2, 3, 4
f4 <- function(x) {
  if (x=='Other') {
    return(0)
  } else if (x=='High School') {
    return(1)
  } else if (x=='Bachelors Degree') {
    return(2)
  } else if (x=='0 - 2 years of graduate school') {
    return(3)
  } else if (x=='> 2 years of graduate school'){
    return(4)
  } else {
    return(NA)
  }
}

d2$Q14 <- sapply(d2$Q14, f4)

# Turn income into 1, 2, 3, 4
f5 <- function(x) {
  if (x=='0 - $50,000') {
    return(1)
  } else if (x=='$50,000 - $100,000') {
    return(2)
  } else if (x=='$100,000 - $150,000') {
    return(3)
  } else if (x=='$150,000 or greater') {
    return(4)
  } else {
    return(NA)
  }
}

d2$Q15 <- sapply(d2$Q15, f5)
```

Check dataframe: 

```{r}
str(d2)
#View(d2)
```

## 1.4 Rename columns for clarity

```{r}
names(d2)
```

```{r}
setnames(d2, old = c("Duration..in.seconds.", "Q1_1","Q3_1", "Q6_1", "Q8_1", "Q10_1","Q12_1", "Q20_1" , "Q5_1" , "Q7_1", "Q9_1" , "Q11_1" , "Q13_1" , "Q18" , "Q19","Q23", "Q17"         , "Q24", "Q33_1" , "Q34_1" , "Q35_1" , "Q36_1" , "Q37_1" , "Q31" ,"Q14",  "Q15", "Q16"), new = c('duration_seconds','AI_educated','AI_attitude', 'control_undesirable', "control_jobs", "control_oversight", "control_recommender", "control_beneficial", "treat_beneficial_1", "treat_undesirable_1", "treat_jobs_1","treat_oversight_1", "treat_recommender_1", "attention_undesirable", "attention_jobs", "attention_oversight", "attention_beneficial", "attention_recommender", "treat_beneficial_2", "treat_undesirable_2", "treat_jobs_2", "treat_oversight_2", "treat_recommender_2", "learn_anything", "education_level", "house_income", "gender" ))
names(d2)
```

## 1.5 Combine 2 treatment columns for each treatment question

```{r}
na.zero <- function (x) {
    x[is.na(x)] <- 0
    return(x)
}
```

```{r}
d2$treat_beneficial_1 <- na.zero(d2$treat_beneficial_1)
d2$treat_beneficial_2 <- na.zero(d2$treat_beneficial_2)
d2$treat_beneficial = d2$treat_beneficial_1 + d2$treat_beneficial_2
d2$treat_beneficial
d2$treat_beneficial[d2$treat_beneficial == 0] <- NA
d2$treat_beneficial
```

```{r}
d2$treat_undesirable_1 <- na.zero(d2$treat_undesirable_1)
d2$treat_undesirable_2 <- na.zero(d2$treat_undesirable_2)
d2$treat_undesirable = d2$treat_undesirable_1 + d2$treat_undesirable_2
d2$treat_undesirable
d2$treat_undesirable[d2$treat_undesirable == 0] <- NA
d2$treat_undesirable
```

```{r}
d2$treat_jobs_1 <- na.zero(d2$treat_jobs_1)
d2$treat_jobs_2 <- na.zero(d2$treat_jobs_2)
d2$treat_jobs = d2$treat_jobs_1 + d2$treat_jobs_2
d2$treat_jobs
d2$treat_jobs[d2$treat_jobs == 0] <- NA
d2$treat_jobs
```

```{r}
d2$treat_oversight_1 <- na.zero(d2$treat_oversight_1)
d2$treat_oversight_2 <- na.zero(d2$treat_oversight_2)
d2$treat_oversight = d2$treat_oversight_1 + d2$treat_oversight_2
d2$treat_oversight
d2$treat_oversight[d2$treat_oversight == 0] <- NA
d2$treat_oversight
```


```{r}
d2$treat_recommender_1 <- na.zero(d2$treat_recommender_1)
d2$treat_recommender_2 <- na.zero(d2$treat_recommender_2)
d2$treat_recommender = d2$treat_recommender_1 + d2$treat_recommender_2
d2$treat_recommender
d2$treat_recommender[d2$treat_recommender == 0] <- NA
d2$treat_recommender
```


```{r}
head(d2)
```

## 1.6 Prepare the Dataframe for regression analysis:

#A. Must have all responses to a question in one column and whether individual was treatment or control for that question in one column.

I wanted to reuse brute force code so i renamed the df legit_data.

```{r}
legit_data <- d2
```

```{r}
legit_data$assignment_beneficial <- 9
legit_data$score_beneficial<- 9

legit_data$assignment_undesirable <- 9
legit_data$score_undesirable<- 9

legit_data$assignment_jobs <- 9
legit_data$score_jobs <- 9

legit_data$assignment_oversight <- 9
legit_data$score_oversight<- 9

legit_data$assignment_recommender <- 9
legit_data$score_recommender<- 9
```


#Create a treatment or control column for beneficial question
```{r}
legit_data[legit_data$control_beneficial == 1, ][, 'assignment_beneficial'] <- 0
legit_data[legit_data$control_beneficial == 2, ][, 'assignment_beneficial'] <- 0
legit_data[legit_data$control_beneficial == 3, ][, 'assignment_beneficial'] <- 0
legit_data[legit_data$control_beneficial == 4, ][, 'assignment_beneficial'] <- 0
legit_data[legit_data$control_beneficial == 5, ][, 'assignment_beneficial'] <- 0
legit_data[is.na(legit_data$control_beneficial), ][, 'assignment_beneficial'] <- 1

legit_data[is.na(legit_data$control_beneficial) & is.na(legit_data$treat_beneficial), ][, 'assignment_beneficial'] <- NA
```
#Merge values for treatment or control beneficial question into one column

```{r}
legit_data[legit_data$treat_beneficial == 1, ][, 'score_beneficial'] <- 1
legit_data[legit_data$treat_beneficial == 2, ][, 'score_beneficial'] <- 2
legit_data[legit_data$treat_beneficial == 3, ][, 'score_beneficial'] <- 3
legit_data[legit_data$treat_beneficial == 4, ][, 'score_beneficial'] <- 4
legit_data[legit_data$treat_beneficial == 5, ][, 'score_beneficial'] <- 5

legit_data[legit_data$control_beneficial == 1, ][, 'score_beneficial'] <- 1
legit_data[legit_data$control_beneficial == 2, ][, 'score_beneficial'] <- 2
legit_data[legit_data$control_beneficial == 3, ][, 'score_beneficial'] <- 3
legit_data[legit_data$control_beneficial == 4, ][, 'score_beneficial'] <- 4
legit_data[legit_data$control_beneficial == 5, ][, 'score_beneficial'] <- 5

legit_data[is.na(legit_data$control_beneficial) & is.na(legit_data$treat_beneficial), ][, 'score_beneficial'] <- NA
```

Same for undesirable
```{r}
legit_data[legit_data$control_undesirable == 1, ][, 'assignment_undesirable'] <- 0
legit_data[legit_data$control_undesirable == 2, ][, 'assignment_undesirable'] <- 0
legit_data[legit_data$control_undesirable == 3, ][, 'assignment_undesirable'] <- 0
legit_data[legit_data$control_undesirable == 4, ][, 'assignment_undesirable'] <- 0
legit_data[legit_data$control_undesirable == 5, ][, 'assignment_undesirable'] <- 0
legit_data[is.na(legit_data$control_undesirable), ][, 'assignment_undesirable'] <- 1

legit_data[is.na(legit_data$control_undesirable) & is.na(legit_data$treat_undesirable), ][, 'assignment_undesirable'] <- NA


legit_data[legit_data$treat_undesirable == 1, ][, 'score_undesirable'] <- 1
legit_data[legit_data$treat_undesirable == 2, ][, 'score_undesirable'] <- 2
legit_data[legit_data$treat_undesirable == 3, ][, 'score_undesirable'] <- 3
legit_data[legit_data$treat_undesirable == 4, ][, 'score_undesirable'] <- 4
legit_data[legit_data$treat_undesirable == 5, ][, 'score_undesirable'] <- 5

legit_data[legit_data$control_undesirable == 1, ][, 'score_undesirable'] <- 1
legit_data[legit_data$control_undesirable == 2, ][, 'score_undesirable'] <- 2
legit_data[legit_data$control_undesirable == 3, ][, 'score_undesirable'] <- 3
legit_data[legit_data$control_undesirable == 4, ][, 'score_undesirable'] <- 4
legit_data[legit_data$control_undesirable == 5, ][, 'score_undesirable'] <- 5

legit_data[is.na(legit_data$control_undesirable) & is.na(legit_data$treat_undesirable), ][, 'score_undesirable'] <- NA

```


Same for jobs
```{r}
legit_data[legit_data$control_jobs == 1, ][, 'assignment_jobs'] <- 0
legit_data[legit_data$control_jobs == 2, ][, 'assignment_jobs'] <- 0
legit_data[legit_data$control_jobs == 3, ][, 'assignment_jobs'] <- 0
legit_data[legit_data$control_jobs == 4, ][, 'assignment_jobs'] <- 0
legit_data[legit_data$control_jobs == 5, ][, 'assignment_jobs'] <- 0
legit_data[is.na(legit_data$control_jobs), ][, 'assignment_jobs'] <- 1

legit_data[is.na(legit_data$control_jobs) & is.na(legit_data$treat_jobs), ][, 'assignment_jobs'] <- NA


legit_data[legit_data$treat_jobs == 1, ][, 'score_jobs'] <- 1
legit_data[legit_data$treat_jobs == 2, ][, 'score_jobs'] <- 2
legit_data[legit_data$treat_jobs == 3, ][, 'score_jobs'] <- 3
legit_data[legit_data$treat_jobs == 4, ][, 'score_jobs'] <- 4
legit_data[legit_data$treat_jobs == 5, ][, 'score_jobs'] <- 5

legit_data[legit_data$control_jobs == 1, ][, 'score_jobs'] <- 1
legit_data[legit_data$control_jobs == 2, ][, 'score_jobs'] <- 2
legit_data[legit_data$control_jobs == 3, ][, 'score_jobs'] <- 3
legit_data[legit_data$control_jobs == 4, ][, 'score_jobs'] <- 4
legit_data[legit_data$control_jobs == 5, ][, 'score_jobs'] <- 5

legit_data[is.na(legit_data$control_jobs) & is.na(legit_data$treat_jobs), ][, 'score_jobs'] <- NA
```


Same for oversight
```{r}
legit_data[legit_data$control_oversight == 1, ][, 'assignment_oversight'] <- 0
legit_data[legit_data$control_oversight == 2, ][, 'assignment_oversight'] <- 0
legit_data[legit_data$control_oversight == 3, ][, 'assignment_oversight'] <- 0
legit_data[legit_data$control_oversight == 4, ][, 'assignment_oversight'] <- 0
legit_data[legit_data$control_oversight == 5, ][, 'assignment_oversight'] <- 0
legit_data[is.na(legit_data$control_oversight), ][, 'assignment_oversight'] <- 1

legit_data[is.na(legit_data$control_oversight) & is.na(legit_data$treat_oversight), ][, 'assignment_oversight'] <- NA

legit_data[legit_data$treat_oversight == 1, ][, 'score_oversight'] <- 1
legit_data[legit_data$treat_oversight == 2, ][, 'score_oversight'] <- 2
legit_data[legit_data$treat_oversight == 3, ][, 'score_oversight'] <- 3
legit_data[legit_data$treat_oversight == 4, ][, 'score_oversight'] <- 4
legit_data[legit_data$treat_oversight == 5, ][, 'score_oversight'] <- 5

legit_data[legit_data$control_oversight == 1, ][, 'score_oversight'] <- 1
legit_data[legit_data$control_oversight == 2, ][, 'score_oversight'] <- 2
legit_data[legit_data$control_oversight == 3, ][, 'score_oversight'] <- 3
legit_data[legit_data$control_oversight == 4, ][, 'score_oversight'] <- 4
legit_data[legit_data$control_oversight == 5, ][, 'score_oversight'] <- 5

legit_data[is.na(legit_data$control_oversight) & is.na(legit_data$treat_oversight), ][, 'score_oversight'] <- NA
```

Same for recommender
```{r}
legit_data[legit_data$control_recommender == 1, ][, 'assignment_recommender'] <- 0
legit_data[legit_data$control_recommender == 2, ][, 'assignment_recommender'] <- 0
legit_data[legit_data$control_recommender == 3, ][, 'assignment_recommender'] <- 0
legit_data[legit_data$control_recommender == 4, ][, 'assignment_recommender'] <- 0
legit_data[legit_data$control_recommender == 5, ][, 'assignment_recommender'] <- 0
legit_data[is.na(legit_data$control_recommender), ][, 'assignment_recommender'] <- 1

legit_data[is.na(legit_data$control_recommender) & is.na(legit_data$treat_recommender), ][, 'assignment_recommender'] <- NA

legit_data[legit_data$treat_recommender == 1, ][, 'score_recommender'] <- 1
legit_data[legit_data$treat_recommender == 2, ][, 'score_recommender'] <- 2
legit_data[legit_data$treat_recommender == 3, ][, 'score_recommender'] <- 3
legit_data[legit_data$treat_recommender == 4, ][, 'score_recommender'] <- 4
legit_data[legit_data$treat_recommender == 5, ][, 'score_recommender'] <- 5

legit_data[legit_data$control_recommender == 1, ][, 'score_recommender'] <- 1
legit_data[legit_data$control_recommender == 2, ][, 'score_recommender'] <- 2
legit_data[legit_data$control_recommender == 3, ][, 'score_recommender'] <- 3
legit_data[legit_data$control_recommender == 4, ][, 'score_recommender'] <- 4
legit_data[legit_data$control_recommender == 5, ][, 'score_recommender'] <- 5

legit_data[is.na(legit_data$control_recommender) & is.na(legit_data$treat_recommender), ][, 'score_recommender'] <- NA
```


```{r}
Survey_df <- legit_data
```



#B. Must recode responses to attention question as correct or not for each question (one column each question) and make a final column that reveals if a person answered their attention question correctly

```{r}
#attention undesirable: right now, 1 is true, 0 is false
#the correct answer is False
Survey_df$attention_undesirable_correct <- 9
Survey_df[Survey_df$attention_undesirable == 0, ][, 'attention_undesirable_correct'] <- 1
Survey_df[Survey_df$attention_undesirable == 1, ][, 'attention_undesirable_correct'] <- 0
Survey_df[is.na(Survey_df$attention_undesirable), ][, 'attention_undesirable_correct'] <- NA
head(Survey_df)
```


```{r}
#attention jobs: right now, 1 is true, 0 is false
#the correct answer is True
Survey_df$attention_jobs_correct <- 9
Survey_df[Survey_df$attention_jobs == 0, ][, 'attention_jobs_correct'] <- 0
Survey_df[Survey_df$attention_jobs == 1, ][, 'attention_jobs_correct'] <- 1
Survey_df[is.na(Survey_df$attention_jobs), ][, 'attention_jobs_correct'] <- NA
head(Survey_df)
```


```{r}
#attention oversight: right now, 1 is true, 0 is false
#the correct answer is False
Survey_df$attention_oversight_correct <- 9
Survey_df[Survey_df$attention_oversight == 0, ][, 'attention_oversight_correct'] <- 1
Survey_df[Survey_df$attention_oversight == 1, ][, 'attention_oversight_correct'] <- 0
Survey_df[is.na(Survey_df$attention_oversight), ][, 'attention_oversight_correct'] <- NA
head(Survey_df)
```

```{r}
#attention recommender: right now, 1 is true, 0 is false
#the correct answer is False
Survey_df$attention_recommender_correct <- 9
Survey_df[Survey_df$attention_recommender == 0, ][, 'attention_recommender_correct'] <- 1
Survey_df[Survey_df$attention_recommender == 1, ][, 'attention_recommender_correct'] <- 0
Survey_df[is.na(Survey_df$attention_recommender), ][, 'attention_recommender_correct'] <- NA
head(Survey_df)
```

```{r}
#attention beneficial: right now, 1 is true, 0 is false
#the correct answer is True
Survey_df$attention_beneficial_correct <- 9
Survey_df[Survey_df$attention_beneficial == 0, ][, 'attention_beneficial_correct'] <- 0
Survey_df[Survey_df$attention_beneficial == 1, ][, 'attention_beneficial_correct'] <- 1
Survey_df[is.na(Survey_df$attention_beneficial), ][, 'attention_beneficial_correct'] <- NA
head(Survey_df)
```



```{r}
Survey_df$attention_beneficial_correct_intermed <- na.zero(Survey_df$attention_beneficial_correct)
Survey_df$attention_jobs_correct_intermed <- na.zero(Survey_df$attention_jobs_correct)
Survey_df$attention_oversight_correct_intermed <- na.zero(Survey_df$attention_oversight_correct)
Survey_df$attention_recommender_correct_intermed <- na.zero(Survey_df$attention_recommender_correct)
Survey_df$attention_undesirable_correct_intermed <- na.zero(Survey_df$attention_undesirable_correct)

Survey_df$attention_correct = Survey_df$attention_beneficial_correct_intermed + Survey_df$attention_jobs_correct_intermed +Survey_df$attention_oversight_correct_intermed+Survey_df$attention_recommender_correct_intermed+Survey_df$attention_undesirable_correct_intermed


Survey_df[is.na(Survey_df$attention_beneficial_correct) & is.na(Survey_df$attention_jobs_correct)& is.na(Survey_df$attention_oversight_correct)& is.na(Survey_df$attention_recommender_correct)& is.na(Survey_df$attention_undesirable_correct), ][, 'attention_correct'] <- NA


head(Survey_df)
```

Examine attention_correct column:

```{r}
summary(Survey_df$attention_correct)
```

Remove intermediate attention correct columns (they have NAs as 0's - misleading):

```{r}
Survey_df <-Survey_df[ , !c("attention_beneficial_correct_intermed","attention_jobs_correct_intermed", "attention_oversight_correct_intermed", "attention_recommender_correct_intermed", "attention_undesirable_correct_intermed") ]
```

```{r}
head(Survey_df)
```


```{r}
View(Survey_df)
```


#Write dataframe to csv

```{r}
write.csv(Survey_df, 'Cleaned_Full_Survey_dataV1.csv', row.names=FALSE)
```

