---
title: 'W241: AI Project Final Survey'
subtitle: 'Data Cleaning V2'
author: "Zhaoning Yu"
date: "4/08/2018"
output: pdf_document
---

```{r setup, include=FALSE, message=FALSE}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
# knitr::opts_chunk$set(echo = TRUE)

# load packages 
library(Hmisc)              # describe()
library(data.table)
library(foreign)            # ??? what does this package do ????????
library(sandwich)           # vcovHC for robust SE calculation
library(lmtest)             # coeftest 
library(AER)                # ivreg
library(multiwayvcov)       # cluster.vcov()
```


# 1. Read Data

## 1.1 Read Data

First read the cleaned full survey data from KH:

```{r}
rm(list=ls())

d1 <- fread('./Cleaned_Full_Survey_dataV1.csv')
head(d1)
```

### 1.2 Create a factor column for attention question 

```{r}
# create indicator vectors to indicate the attention question type
t1 <- 1*!is.na(d1$attention_undesirable) 
t2 <- 2*!is.na(d1$attention_jobs) 
t3 <- 3*!is.na(d1$attention_oversight) 
t4 <- 4*!is.na(d1$attention_recommender) 
t5 <- 5*!is.na(d1$attention_beneficial) 

# add a vector column for attention question
d1$attention_question_code <- t1 + t2 + t3 + t4 + t5
d1$attention_question <- as.factor(t1 + t2 + t3 + t4 + t5)

# rename the levels
levels(d1$attention_question)[levels(d1$attention_question)=="1"] <- "undesirable"
levels(d1$attention_question)[levels(d1$attention_question)=="2"] <- "jobs"
levels(d1$attention_question)[levels(d1$attention_question)=="3"] <- "oversight"
levels(d1$attention_question)[levels(d1$attention_question)=="4"] <- "recommender"
levels(d1$attention_question)[levels(d1$attention_question)=="5"] <- "beneficial"

# levels(d1$attention_question)[levels(d1$attention_question)=="0"] <- "what"
```

## 1.3 Remove some columns and re-arrange:

### Columns that are removed

- "Progress" column has a single value of 100
- "Finished" column has a single value of 1
- "RecordedDate" column has the same information as "EndDate" (+1 second)

### Note:

- "Assignment_##" columns are indicator whether subject assigned to treatment or control for each question
- "Score_##" columns are answers for the question (as control or treatment depending on assignment)

```{r}
d2 <- subset(d1, select=c(ResponseId, mTurkCode, 
                          IPAddress, LocationLatitude, LocationLongitude,
                          StartDate, EndDate, duration_seconds, 
                          gender, education_level, house_income,
                          AI_educated, AI_attitude, learn_anything,
                          assignment_undesirable, assignment_jobs, assignment_oversight, assignment_recommender, assignment_beneficial,
                          score_undesirable, score_jobs, score_oversight, score_recommender, score_beneficial,
                          control_undesirable, control_jobs, control_oversight, control_recommender, control_beneficial,
                          treat_undesirable, treat_jobs, treat_oversight, treat_recommender, treat_beneficial,
                          attention_question_code, attention_question, attention_correct))
str(d2)
```
## 1.4 Convert StartDate and EndDate strings to datetime?

## 1.5 Write dataframe to csv and check result

```{r}
# write.csv(d2, 'Cleaned_Full_Survey_dataV2.csv', row.names=FALSE)
# d3 <- fread('./Cleaned_Full_Survey_dataV2.csv')
# str(d3)
```



# 2. EDA
```{r}
hist(d2[d2$duration_seconds<1000]$duration_seconds, breaks=50)
```

